---
title: "Analyse Family Mobility on Children's Educational Attainment"
author: "Zhang Yicheng"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stargazer)  # regression outputs
library(broom)      # tidy function: statistical outputs into tibbles
library(kableExtra) # make-up tables
library(rstatix)
library(ggpubr)
library(gridExtra)
library(knitr)
library(readr)
library(AER)
library(ggplot2)
options(pillar.sigfig = 3)
library(magrittr)
library(haven)
library(lfe)
library(msir)
```


```{r}
# Loading data
edu_data <- read_csv("/Users/zhangyicheng/Library/CloudStorage/OneDrive-TheUniversityofChicago/Final_Project/data/clean/fullsample_output.csv", show_col_types = FALSE)

# Creating age group dummies
edu_data <- edu_data %>%
  mutate(age_gp6 = ifelse(edu_data$age == 6, 1, 0)) %>%
  mutate(age_gp7t8 = ifelse((edu_data$age <= 8) & (7 <= edu_data$age), 1, 0)) %>%
  mutate(age_gp9t12 = ifelse((edu_data$age <= 12) & (9 <= edu_data$age), 1, 0)) %>%
  mutate(age_gp6t12 = ifelse((edu_data$age <= 12) & (6 <= edu_data$age), 1, 0)) %>%
  mutate(age_gp13t15 = ifelse((edu_data$age <= 15) & (12 < edu_data$age), 1, 0)) %>%
  mutate(age_gp16t18 = ifelse((edu_data$age <= 18) & (16 <= edu_data$age), 1, 0)) %>%
  filter((fam_income < 100000) & (fam_income > 2000))
```

# Statistics
### Data Distribution
```{r}
par(mfrow=c(1,2))
hist(edu_data$fam_income, freq = FALSE, 
     xlim = c(min(edu_data$fam_income), max(edu_data$fam_income)), 
     ylim = c(0, 0.00005), breaks = 30)
hist(edu_data$income25_35p, freq = FALSE, 
     xlim = c(min(edu_data$fam_income), max(edu_data$fam_income)), 
     ylim = c(0, 0.00005), breaks = 30)
```
\newpage

###  Discriptive Statistics
```{r results='asis', message=FALSE}
regdata <- edu_data %>%
  select(edu, mov, sex, race, age, fam_income, dad_edu, mom_edu, year5, state5,
         age_gp6, age_gp6t12, age_gp7t8, age_gp9t12, age_gp13t15, age_gp16t18) %>%
  na.omit()
stargazer(as.data.frame(regdata), type = 'latex', title = 'Descriptive statistics')
```
# Empirical Results

## Edu - OLS
### Baseline -yrs
```{r results='asis', message=FALSE}
attach(regdata)

naive_reg <- felm(formula = edu ~ mov | year5 + state5)
simple_reg <- felm(formula = edu ~ mov + sex + race | age + year5 + state5 |0| state5 )
fixed_reg <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu | age + year5 + state5 |0| state5 )
fixed_reg3 <- felm(formula = edu ~ mov*age + sex + race  + log(fam_income) + dad_edu + mom_edu |year5 + state5 |0| state5 )
fixed_reg2 <- felm(formula = edu ~ mov*sex + race  + log(fam_income) + dad_edu + mom_edu |age + year5 + state5 |0| state5 )

stargazer(naive_reg, simple_reg, fixed_reg, fixed_reg2, fixed_reg3, 
          type = 'latex',
          header = FALSE,
          title = "Mobility Effects on Education Attainment",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          add.lines=list(c('Age dummies', 'No','Yes','Yes','Yes','No'),
                         c('Year FE', 'Yes','Yes','Yes','Yes','Yes'),
                         c('State FE', 'Yes','Yes','Yes','Yes','Yes')),
          df = FALSE)
detach(regdata)
```

### Interaction - age grp
```{r results='asis', message=FALSE}
attach(regdata)

fixed_reg2 <- felm(formula = edu ~ mov + age_gp6 + age_gp7t8 + age_gp9t12 + age_gp13t15
                    + log(fam_income) + dad_edu + mom_edu + sex + race | year5 + state5 |0|state5)

int_age_reg <- felm(formula = edu ~ mov*age_gp6 + mov*age_gp7t8 + mov*age_gp9t12 + mov*age_gp13t15 + log(fam_income) + dad_edu + mom_edu + sex + race | year5 + state5 |0|state5)

stargazer(fixed_reg2, int_age_reg,
          type = "latex",
          header = FALSE,
          title = "Mobility effects on Education Attainment (interacted with age group)",
          column.labels = c('$(1)$','$(2)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          add.lines=list(c('Birth Year FE', 'Yes','Yes'),
               c('State FE', 'Yes','Yes')),
          df = FALSE)
detach(regdata)
```
### Cross States/Regions Relocation
```{r}
regdata <- edu_data %>%
  select(edu, mov, sex, race, age, fam_income, dad_edu, mom_edu, year5, state5,
         xstate, xreg) %>%
  na.omit()
across_reg <- regdata %>%
  filter((xreg == TRUE)&(mov==1)|(mov==0)) 
not_across_reg <- regdata %>%
  filter((xreg == FALSE)&(mov==1)|(mov==0)) 
across_state <- regdata %>%
  filter((xstate == TRUE)&(mov==1)|(mov==0)) 
not_across_state <- regdata %>%
  filter((xstate == FALSE)&(mov==1)|(mov==0)) 

fixed_reg0 <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  | age + year5 + state5 |0| state5, data = regdata)
fixed_reg1 <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  | age + year5 + state5 |0| state5, data = across_state)
fixed_reg2 <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  | age + year5 + state5 |0| state5, data = not_across_state)
fixed_reg3 <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  | age + year5 + state5 |0| state5, data = across_reg)
fixed_reg4 <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  | age + year5 + state5 |0| state5, data = not_across_reg)

stargazer(fixed_reg0, fixed_reg1, fixed_reg2, fixed_reg3, fixed_reg4, 
          type = 'latex',
          header = FALSE,
          title = "Mobility Effects on Education Attainment",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          add.lines=list(c('Type of move', 'Full sample', 'Across state','Within state','Across region','Within region'),
                          c('Age dummies', 'Yes','Yes','Yes','Yes','Yes'),
                         c('Year FE', 'Yes','Yes','Yes','Yes','Yes'),
                         c('State FE', 'Yes','Yes','Yes','Yes','Yes')),
          df = FALSE)

```
\newpage


## Edu - IV

### Mom-age RAW Visualization
```{r}
### IV Visualization for mom_age ###
iv_data <- edu_data %>%
  select(edu, mov, nmov, sex, race, age, fam_income, dad_edu, mom_edu, mom_age, year5, state5) %>%
  na.omit()

mom_df <- iv_data %>% 
  mutate(mom_gp2025 = ifelse((20 <= iv_data$mom_age) & (iv_data$mom_age <= 25), 1, 0)) %>%
  mutate(mom_gp2630 = ifelse((26 <= iv_data$mom_age) & (iv_data$mom_age <= 30), 1, 0)) %>%
  mutate(mom_gp3135 = ifelse((31 <= iv_data$mom_age) & (iv_data$mom_age <= 35), 1, 0)) %>%
  mutate(mom_gp31p = ifelse(31 < iv_data$mom_age, 1, 0)) %>%
  mutate(mom_gp35p = ifelse(35 < iv_data$mom_age, 1, 0)) %>%
  filter((20 <= iv_data$mom_age) & (iv_data$mom_age <= 45))


mom_iv_df = mom_df %>%
  group_by(mom_age) %>% 
  dplyr::summarise(move = mean(mov), 
                   nmove = mean(nmov),
                   mom_age = median(mom_age),
                   mean_edu = mean(edu))

par(mfrow=c(2,2))

par(pin = c(2, 2))
hist(mom_df$mom_age, freq = FALSE, col = rgb(1, 0.4, 0.4, alpha = 0.15), 
     xlab = "mom age", ylab = "density", main = "First stage", breaks = 25)
par(new = TRUE)
plot(mom_iv_df$mom_age, mom_iv_df$move,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 1, col = 'black')
axis(side = 4) # Add right y-axis
mtext("Prob to Move", side = 4, line = 3) # Add right y-axis label

hist(mom_df$mom_age, freq = FALSE, col = rgb(1, 0.4, 0.4, alpha = 0.15), 
     xlab = "mom age", ylab = "density", main = "Reduced form", breaks = 25)
par(new = TRUE)
plot(mom_iv_df$mom_age, mom_iv_df$mean_edu,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 1, col = 'black')
axis(side = 4)
mtext("child edu", side = 4, line = 3)
```

### Mom_age results & Visualize
```{r results='asis', message=FALSE, image_height = 7}
attach(mom_df)

baseline <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  |year5 + state5 + age|0| state5)


first_stage_reg <- felm(formula = mov ~ mom_age + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + state5 + age|0|state5)
fitted_values <- first_stage_reg$fitted.values
fit <- lm(fitted_values ~ mom_df$mom_age)


par(mfrow=c(1,2))
par(pin = c(2, 2))
hist(mom_df$mom_age, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "mom age", ylab = "density", main = "First stage", breaks = 25)
par(new = TRUE)
plot(fit$fitted.values ~ mom_df$mom_age,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 0, col = 'white',
     ylim = c(0, 1))
l<- loess.sd(fitted_values ~ mom_df$mom_age, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)
axis(side = 4) # Add right y-axis
mtext("Prob to Move", side = 4, line = 3) # Add right y-axis label


second_stage_reg <- felm(formula = edu ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + state5 + age |(mov ~ mom_age)|state5)
fitted_values <- second_stage_reg$fitted.values
par(pin = c(2, 2))
hist(mom_df$mom_age, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "mom age", ylab = "density", main = "Reduced form", breaks = 25)
par(new = TRUE)
plot(fitted_values ~ mom_df$mom_age,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 0, col = 'grey',
     ylim = c(9, 17))
l<- loess.sd(fitted_values ~ mom_df$mom_age, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)
axis(side = 4)
mtext("child edu", side = 4, line = 3)


Fstat0 <- summary(baseline)$F.fstat 
Fstat1 <- summary(first_stage_reg)$F.fstat 
Fstat2 <- summary(second_stage_reg)$F.fstat 
stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars1,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))


stargazer(baseline, first_stage_reg, second_stage_reg,
          type = "latex",
          header = FALSE,
          title = "Mom's age as IV",
          column.labels = c('baseline','$first stage$','$second stage$'),
          colnames = FALSE,
          model.numbers = FALSE,
          add.lines=list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",sep=""),note0,note1,note2), 
                         c('Age dummies', 'Yes','Yes','Yes'),
                         c('Birth Year FE', 'Yes','Yes','Yes'),
                       c('State FE', 'Yes','Yes','Yes')),
          df = FALSE)

```
### Mom-age group Overfit
```{r results='asis', message=FALSE}
attach(mom_df)
first_stage_reg <- felm(formula = mov ~ mom_gp2025 + mom_gp2630 + mom_gp3135 + log(fam_income) + dad_edu + mom_edu + sex + race| age + year5 + state5 |0|state5)

# Extract the fitted values
fitted_values <- first_stage_reg$fitted.values

fit <- lm(fitted_values ~ mom_df$mom_age)
par(mfrow=c(1,2))
par(pin = c(2, 2))
hist(mom_df$mom_age, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "mom age", ylab = "density", main = "First stage", breaks = 25)
par(new = TRUE)
plot(fit$fitted.values ~ mom_df$mom_age,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 0, col = 'white')
l<- loess.sd(fitted_values ~ mom_df$mom_age, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)

axis(side = 4) # Add right y-axis
mtext("Prob to Move", side = 4, line = 3) # Add right y-axis label

second_stage_reg <- felm(formula = edu ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + state5 |(mov ~ mom_gp2025 + mom_gp2630 + mom_gp3135 ) |state5)

# Extract the fitted values
fitted_values <- second_stage_reg$fitted.values

par(pin = c(2, 2))
hist(mom_df$mom_age, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "mom age", ylab = "density", main = "Reduced form", breaks = 25)
par(new = TRUE)

plot(fitted_values ~ mom_df$mom_age,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 0, col = 'grey')
l<- loess.sd(fitted_values ~ mom_df$mom_age, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)

axis(side = 4)
mtext("child edu", side = 4, line = 3)

stargazer(first_stage_reg, second_stage_reg,
          type = "latex",
          header = FALSE,
          title = "Mom's age as IV",
          column.labels = c('$first stage$','$second stage$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE)

```
### Mom-age group Onefit
```{r results='asis', message=FALSE}
attach(mom_df)
first_stage_reg1 <- felm(formula = mov ~ mom_gp2025 + log(fam_income) + dad_edu + mom_edu + sex + race| age + year5 + state5 |0|state5)
first_stage_reg2 <- felm(formula = mov ~ mom_gp2630 + log(fam_income) + dad_edu + mom_edu + sex + race| age + year5 + state5 |0|state5)
first_stage_reg3 <- felm(formula = mov ~ mom_gp3135 + log(fam_income) + dad_edu + mom_edu + sex + race| age + year5 + state5 |0|state5)


Fstat0 <- summary(first_stage_reg1)$F.fstat 
Fstat1 <- summary(first_stage_reg2)$F.fstat 
Fstat2 <- summary(first_stage_reg3)$F.fstat 

stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))

note0 <- c(paste(round(Fstat0[1],3),stars1,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))


stargazer(first_stage_reg1,first_stage_reg2,first_stage_reg3,
          type = "latex",
          header = FALSE,
          title = "First stage: Discretized Mother's age",
          column.labels = c('(1)','$(2)$','$(3)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          add.lines=list(c("Mom's age group", "20-25", "26-30", "31-35"),
                        c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",sep=""),note0,note1,note2), 
                         c('Age dummies', 'Yes','Yes','Yes'),
                         c('Birth Year FE', 'Yes','Yes','Yes'),
                       c('State FE', 'Yes','Yes','Yes')),
          df = FALSE)
detach(mom_df)
```

```{r results='asis', message=FALSE}
attach(mom_df)
first_stage_reg1 <- felm(formula = mov ~ mom_gp2025 + log(fam_income) + dad_edu + mom_edu + sex + race| age + year5 + state5 |0|state5)
second_stage_reg1 <- felm(formula = edu ~ sex + race + log(fam_income) + dad_edu + mom_edu | age + year5 + state5 |(mov ~ mom_gp2025) |state5)

first_stage_reg2 <- felm(formula = mov ~ mom_gp2630 + log(fam_income) + dad_edu + mom_edu + sex + race| age + year5 + state5 |0|state5)
second_stage_reg2 <- felm(formula = edu ~ sex + race + log(fam_income) + dad_edu + mom_edu |age + year5 + state5 |(mov ~  mom_gp2630 ) |state5)

first_stage_reg3 <- felm(formula = mov ~ mom_gp3135 + log(fam_income) + dad_edu + mom_edu + sex + race| age + year5 + state5 |0|state5)
second_stage_reg3 <- felm(formula = edu ~ sex + race + log(fam_income) + dad_edu + mom_edu |age + year5 + state5 |(mov ~  mom_gp3135 ) |state5)
stargazer(first_stage_reg1, second_stage_reg1,first_stage_reg2, second_stage_reg2,first_stage_reg3, second_stage_reg3,
          type = "latex",
          header = FALSE,
          title = "Mom's age as IV",
          column.labels = c('$1st stage$','$2nd stage$','$1st stage$','$2nd stage$','$1st stage$','$2nd stage$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE)
detach(mom_df)
```
### Number of move in First stage
```{r results='asis', message=FALSE}
attach(mom_df)
first_stage_reg <- felm(formula = nmov ~ mom_age + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + state5 |0|state5)

# Extract the fitted values
fitted_values <- first_stage_reg$fitted.values
fit <- lm(fitted_values ~ mom_df$mom_age)

par(mfrow=c(1,2))
par(pin = c(2, 2))
hist(mom_df$mom_age, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "mom age", ylab = "density", main = "First stage", breaks = 25)
par(new = TRUE)
plot(fit$fitted.values ~ mom_df$mom_age,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 0, col = 'white')
l<- loess.sd(fitted_values ~ mom_df$mom_age, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)
axis(side = 4) # Add right y-axis
mtext("Prob to Move", side = 4, line = 3) # Add right y-axis label

## THIS IS WEIRD
second_stage_reg <- felm(formula = edu ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + state5 |(nmov + I(nmov^2) ~ mom_age)|state5)

# Extract the fitted values
fitted_values <- second_stage_reg$fitted.values

par(pin = c(2, 2))
hist(mom_df$mom_age, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "mom age", ylab = "density", main = "Reduced form", breaks = 25)
par(new = TRUE)

plot(fitted_values ~ mom_df$mom_age,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 0.5, col = 'grey')
l<- loess.sd(fitted_values ~ mom_df$mom_age, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)

axis(side = 4)
mtext("child edu", side = 4, line = 3)

stargazer(first_stage_reg, second_stage_reg,
          type = "latex",
          header = FALSE,
          title = "Mom's age as IV",
          column.labels = c('$first stage$','$second stage$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE)
detach(mom_df)

```

### Visulize Income - momage iv 
```{r}
iv_data <- edu_data %>%
  select(income25_35p, edu, mov, sex, race, age, fam_income, dad_edu, mom_edu, mom_age, year5, state5) %>%
  na.omit()

mom_df = iv_data %>% 
  filter((20 <= mom_age) & (mom_age <= 45))

mom_iv_df = mom_df %>%
  group_by(mom_age) %>% 
  dplyr::summarise(move = mean(mov), 
                   mom_age = median(mom_age),
                   mean_edu = mean(edu))
attach(mom_df)
first_stage_reg <- felm(formula = mov ~ mom_age + log(fam_income) + dad_edu + mom_edu + sex + race| age + year5 + state5 |0|state5)

# Extract the fitted values
fitted_values <- first_stage_reg$fitted.values

fit <- lm(fitted_values ~ mom_df$mom_age)
par(mfrow=c(1,2))
par(pin = c(2, 2))
hist(mom_df$mom_age, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "mom age", ylab = "density", main = "First stage", breaks = 25)
par(new = TRUE)
plot(fit$fitted.values ~ mom_df$mom_age,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 0, col = 'white',
     ylim = c(0, 1))
l<- loess.sd(fitted_values ~ mom_df$mom_age, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)
axis(side = 4) # Add right y-axis
mtext("Prob to Move", side = 4, line = 3) # Add right y-axis label

second_stage_reg <- felm(formula = log(income25_35p) ~ sex + race + log(fam_income) + dad_edu + mom_edu |age + year5 + state5 |(mov ~ mom_age)|state5)

# Extract the fitted values
fitted_values <- second_stage_reg$fitted.values

par(pin = c(2, 2))
hist(mom_df$mom_age, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "mom age", ylab = "density", main = "Reduced form", breaks = 25)
par(new = TRUE)

plot(fitted_values ~ mom_df$mom_age,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 0, col = 'grey')
l<- loess.sd(fitted_values ~ mom_df$mom_age, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)
axis(side = 4)
mtext("log(incoome25-35p)", side = 4, line = 3)

stargazer(first_stage_reg, second_stage_reg,
          type = "latex",
          header = FALSE,
          title = "Mom's age as IV",
          column.labels = c('$first stage$','$second stage$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE)
```
### Number of regions IV RAW Visualization
```{r}
### IV Visualization for number of stage ###
iv_data <- edu_data %>%
  select(edu, mov, sex, race, age, fam_income, dad_edu, mom_edu, nreg, year5, state5) %>%
  mutate(nreg1=ifelse(nreg==1,1,0)) %>%
  mutate(nreg2=ifelse(nreg==2,1,0)) %>%
  mutate(nreg2p=ifelse(nreg>2,1,0)) %>%
  na.omit()

nreg_df = iv_data %>% 
  filter(nreg <= 5)

nreg_iv_df = nreg_df %>%
  group_by(nreg) %>% 
  dplyr::summarise(move = mean(mov), 
                   hd_nreg = median(nreg),
                   mean_edu = mean(edu))

par(mfrow=c(1,2))
par(pin = c(2, 2))
####
hist(nreg_df$nreg, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "number of region", ylab = "density", main = "First stage")
par(new = TRUE)
plot(nreg_iv_df$hd_nreg, nreg_iv_df$move,
     xaxt = "n", yaxt = "n",ann = FALSE, type = "l", lwd = 2)
axis(side = 4) # Add right y-axis
mtext("Prob to Move", side = 4, line = 3) # Add right y-axis label

####
hist(nreg_df$nreg, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "number of region", ylab = "density", main = "Reduced form")
par(new = TRUE)
plot(nreg_iv_df$hd_nreg, nreg_iv_df$mean_edu,
     xaxt = "n", yaxt = "n",ann = FALSE, type = "l", lwd = 2)
axis(side = 4)
mtext("child edu", side = 4, line = 3)
```

### Number of regions IV results
```{r results='asis', message=FALSE}
attach(nreg_df)

baseline <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  |age + year5 + state5 |0| state5)
first_stage_reg <- felm(formula = mov ~ nreg + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + state5 + age|0|state5)

fitted_values <- first_stage_reg$fitted.values
par(mfrow=c(1,2))
par(pin = c(2, 2))
hist(nreg_df$nreg, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "number of regions", ylab = "density", main = "First stage", breaks = 25)
par(new = TRUE)
plot(fitted_values ~ nreg_df$nreg,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 0, col = 'white',
     ylim = c(0, 1))
l<- loess.sd(fitted_values ~ nreg_df$nreg, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)
axis(side = 4) # Add right y-axis
mtext("Prob to Move", side = 4, line = 3) # Add right y-axis label


second_stage_reg <- felm(formula = edu ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + state5 + age | (mov ~ nreg) |state5 )
fitted_values <- second_stage_reg$fitted.values
par(pin = c(2, 2))
hist(nreg_df$nreg, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "number of regions", ylab = "density", main = "Reduced form", breaks = 25)
par(new = TRUE)
plot(fitted_values ~ nreg_df$nreg,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 1, col = 'gray')
l<- loess.sd(fitted_values ~ nreg_df$nreg, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)
axis(side = 4)
mtext("child edu", side = 4, line = 3)

Fstat0 <- summary(baseline)$F.fstat 
Fstat1 <- summary(first_stage_reg)$F.fstat 
Fstat2 <- summary(second_stage_reg)$F.fstat 
stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars1,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))

stargazer(baseline, first_stage_reg, second_stage_reg,
          type = "latex",
          header = FALSE,
          title = "Number of Regions as IV",
          column.labels = c('baseline','$first stage$','$second stage$'),
          colnames = FALSE,
          model.numbers = FALSE,
          add.lines=list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",sep=""),note0,note1,note2),
                         c('Age dummies', 'Yes','Yes','Yes'),
                         c('Birth Year FE', 'Yes','Yes','Yes'),
                       c('State FE', 'Yes','Yes','Yes')),
          df = FALSE)

detach(nreg_df)
```

### Number of STATEs IV RAW Visualization
```{r}
### IV Visualization for number of state ###
iv_data <- edu_data %>%
  select(edu, mov, sex, race, age, fam_income, dad_edu, mom_edu, nstate, year5, state5) %>%
  mutate(nstate12=ifelse(nstate<=2,1,0)) %>%
  mutate(nstate34=ifelse((nstate<=4)&(nstate<=3),1,0)) %>%
  # mutate(nstate5=ifelse(nreg>2,1,0)) %>%
  na.omit()

nreg_df = iv_data %>% 
  filter(nstate <= 12)

nreg_iv_df = nreg_df %>%
  group_by(nstate) %>% 
  dplyr::summarise(move = mean(mov), 
                   hd_nreg = median(nstate),
                   mean_edu = mean(edu))

par(mfrow=c(1,2))
par(pin = c(2, 2))
####
hist(nreg_df$nstate, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "number of region", ylab = "density", main = "First stage")
par(new = TRUE)
plot(nreg_iv_df$hd_nreg, nreg_iv_df$move,
     xaxt = "n", yaxt = "n",ann = FALSE, type = "l", lwd = 2,
     ylim = c(0, 1))
axis(side = 4) # Add right y-axis
mtext("Prob to Move", side = 4, line = 3) # Add right y-axis label

####
hist(nreg_df$nstate, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "number of region", ylab = "density", main = "Reduced form")
par(new = TRUE)
plot(nreg_iv_df$hd_nreg, nreg_iv_df$mean_edu,
     xaxt = "n", yaxt = "n",ann = FALSE, type = "l", lwd = 2)
axis(side = 4)
mtext("child edu", side = 4, line = 3)
```
### Number of STATEs IV Results
```{r results='asis', message=FALSE}
attach(nreg_df)

baseline <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  |year5 + state5 + age |0| state5)

first_stage_reg <- felm(formula = mov ~ nstate12 + nstate34 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + age + state5  |0|state5)

fitted_values <- first_stage_reg$fitted.values
par(mfrow=c(1,2))
par(pin = c(2, 2))
hist(nreg_df$nstate, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "number of states", ylab = "density", main = "First stage", breaks = 25)
par(new = TRUE)
plot(fitted_values ~ nreg_df$nstate,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 0, col = 'grey',
     ylim = c(0, 1))
l<- loess.sd(fitted_values ~ nreg_df$nstate, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)
axis(side = 4) # Add right y-axis
mtext("Prob to Move", side = 4, line = 3) # Add right y-axis label


second_stage_reg <- felm(formula = edu ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + state5 + age | (mov ~ nstate12 + nstate34) |state5 )
fitted_values <- second_stage_reg$fitted.values
par(pin = c(2, 2))
hist(nreg_df$nstate, freq = FALSE, col = rgb(1, 0.75, 0.8, alpha = 0.3), 
     xlab = "number of states", ylab = "density", main = "Reduced form", breaks = 25)
par(new = TRUE)
plot(fitted_values ~ nreg_df$nstate,
     xaxt = "n", yaxt = "n",ann = FALSE, lwd = 1, col = 'gray')
l<- loess.sd(fitted_values ~ nreg_df$nstate, nsigma = 1.625)
lines(l$x, l$y, lwd = 2)
lines(l$x, l$upper, lty=2)
lines(l$x, l$lower, lty=2)
axis(side = 4)
mtext("child edu", side = 4, line = 3)


Fstat0 <- summary(baseline)$F.fstat 
Fstat1 <- summary(first_stage_reg)$F.fstat 
Fstat2 <- summary(second_stage_reg)$F.fstat 
stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars1,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))

stargazer(baseline, first_stage_reg, second_stage_reg,
          type = "latex",
          header = FALSE,
          title = "Number of States as IV",
          column.labels = c('baseline','$first stage$','$second stage$'),
          colnames = FALSE,
          model.numbers = FALSE,
          add.lines=list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",sep=""),note0,note1,note2), 
                          c('Age dummies', 'Yes','Yes','Yes'),
                         c('Birth Year FE', 'Yes','Yes','Yes'),
                       c('State FE', 'Yes','Yes','Yes')),
          df = FALSE)
detach(nreg_df)
```
## Auxiliary Regressions 
### Number of move
```{r results='asis', message=FALSE}
aux_data <- edu_data %>%
  select(edu, nmov, mov, sex, race, age, fam_income, dad_edu, mom_edu, year5, state5,
         age_gp6, age_gp7t8, age_gp9t12, age_gp13t15, age_gp16t18) %>%
  mutate(move3p = ifelse(nmov>3, 1, 0)) %>%
  mutate(move3 = ifelse(nmov == 3, 1, 0)) %>%
  mutate(move2 = ifelse(nmov == 2, 1, 0)) %>%
  mutate(move1 = ifelse(nmov == 1, 1, 0)) %>%
  na.omit()

attach(aux_data)
fixed_reg <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  |year5 + state5 + age |0| state5)
fixed_reg1 <- felm(formula = edu ~ nmov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  |year5 + state5 + age |0| state5)
fixed_reg2 <- felm(formula = edu ~ nmov + I(nmov^2) + sex + race + log(fam_income) + dad_edu + mom_edu 
                  |year5 + state5 + age |0| state5)
fixed_reg3 <- felm(formula = edu ~ move1 + move2 + move3 + move3p + sex + race  + log(fam_income) + dad_edu + mom_edu 
                  |year5 + state5 + age |0| state5)

stargazer(fixed_reg, fixed_reg1, fixed_reg2, fixed_reg3,
          type = 'latex',
          header = FALSE,
          title = "Number of time moved",
          column.labels = c('$1$', '$2$', '$3$', '$4$'),
          colnames = FALSE,
          model.numbers = FALSE,
          add.lines=list(c('Age dummies', 'Yes','Yes','Yes','Yes'),
               c('Year FE', 'Yes','Yes','Yes','Yes'),
               c('State FE', 'Yes','Yes','Yes','Yes')),
          df = FALSE)
detach(aux_data)




```

### Reason to move
```{r results='asis', message=FALSE}
reason_data <- edu_data %>%
  select(edu, reason_gp, mov, sex, race, age, fam_income, dad_edu, mom_edu, year5, state5)

reason1_data <- reason_data %>%
  filter((reason_gp == 1)|(mov==0))
reason2_data <- reason_data %>%
  filter((reason_gp == 2)|(mov==0))
reason3_data <- reason_data %>%
  filter((reason_gp == 3)|(mov==0))
reason4_data <- reason_data %>%
  filter((reason_gp == 4)|(mov==0))

reason1_reg <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  |age + year5 + state5 |0| state5, data = reason1_data)
reason2_reg <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  |age + year5 + state5 |0| state5, data = reason2_data)
reason3_reg <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  |age + year5 + state5 |0| state5, data = reason3_data)
reason4_reg <- felm(formula = edu ~ mov + sex + race + log(fam_income) + dad_edu + mom_edu 
                  |age + year5 + state5 |0| state5, data = reason4_data)

stargazer(reason1_reg, reason2_reg, reason3_reg, reason4_reg,
          type = 'latex',
          header = FALSE,
          title = "Effects on Education outcome: Subgroup based on moving reason",
          column.labels = c('$(1)$', '$(2)$', '$(3)$', '$(4)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE)
```