---
title: "Income_ChildMove"
author: "Yicheng Zhang and Sifei Liu"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(stargazer)  # regression outputs
library(broom)      # tidy function: statistical outputs into tibbles
library(kableExtra) # make-up tables
library(rstatix)
library(ggpubr)
library(gridExtra)
library(knitr)
library(readr)
library(AER)
library(ggplot2)
options(pillar.sigfig = 3)
library(magrittr)
library(haven)
library(lfe)
library(texreg)
```

```{r}
# change directory as needed
data <- read_csv("../data/fullsample_output.csv", show_col_types = FALSE)

data <- data %>% 
  mutate(age_gp12 = ifelse(age <= 12, 1, 0))

data <- data %>% 
  mutate(age_gp6 = ifelse((age == 6), 1, 0)) %>%
  mutate(age_gp7t8 = ifelse((age >= 7) & (age <= 8), 1, 0)) %>%
  mutate(age_gp9t10 = ifelse((age >= 9) & (age <= 10), 1, 0)) %>%
  mutate(age_gp11t12 = ifelse((age >= 11) & (age <= 12), 1, 0)) %>%
  mutate(age_gp9t12 = ifelse((age >= 9) & (age <= 12), 1, 0)) %>%
  mutate(age_gp13t14 = ifelse((age >= 13) & (age <= 14), 1, 0)) %>%
  mutate(age_gp15 = ifelse((age == 15), 1, 0)) %>%
  mutate(age_gp13t15 = ifelse((age >= 13) & (age <= 15), 1, 0)) %>%
  mutate(age_gp16t18 = ifelse((age >= 16) & (age <= 18), 1, 0))

data <- data %>%
  mutate(mom_age_gp1 = ifelse((mom_age >= 20 & mom_age < 23), 1, 0)) %>%
  mutate(mom_age_gp2 = ifelse((mom_age >= 23 & mom_age < 27), 1, 0)) %>%
  mutate(mom_age_gp3 = ifelse((mom_age >= 27 & mom_age < 31), 1, 0)) %>%
  mutate(mom_age_gp4 = ifelse((mom_age >= 31 & mom_age < 35), 1, 0)) %>%
  mutate(mom_age_gp5 = ifelse((mom_age >= 35), 1, 0)) %>%
  mutate(mom_age_gp30 = ifelse((mom_age <= 30)&(mom_age >= 23), 1, 0))

data <- data %>%
  mutate(nreg_dum1 = ifelse((nreg == 1), 1, 0)) %>%
  mutate(nreg_dum2 = ifelse((nreg >= 2), 1, 0))

data <- data %>%
  mutate(nstate_dum = ifelse((nstate >= 3), 1, 0)) %>%
  mutate(nstate_dum1 = ifelse((nstate == 1), 1, 0)) %>%
  mutate(nstate_dum2 = ifelse((nstate == 2), 1, 0)) %>%
  mutate(nstate_dum3 = ifelse((nstate == 3), 1, 0)) %>%
  mutate(nstate_dum4 = ifelse((nstate >= 4), 1, 0))

data <- data %>%
  mutate(nmov1 = ifelse((nmov == 1), 1, 0)) %>%
  mutate(nmov2 = ifelse((nmov == 2), 1, 0)) %>%
  mutate(nmov3 = ifelse((nmov == 3), 1, 0)) %>%
  mutate(nmov4 = ifelse((nmov >= 4), 1, 0))

```

# Summary Statistics

## Table 5:Summary

```{r}
df <- data %>% 
  select("income25_35p","mov","edu","fam_income", "dad_edu", "mom_edu",'mom_age',
          'sex','race','age',"year5","reg5","mom_age") %>%
  filter((fam_income > 200) & (income25_35p > 100)) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,age,year5,reg5,mom_age))
stargazer(as.data.frame(df), type = "latex", title="Descriptive statistics", digits=2)
```

# Empirical Results

## Income - Baseline OLS
### Table 6: Income avg 25-35p

```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100)) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))

attach(regdata)

reg0 <- felm(formula = log(income25_35p) ~ mov | year5|0|0)
reg1 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race|year5 + age|0|0)
reg2 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race|year5 + reg5 + age|0|0) 
reg_s <- felm(formula = log(income25_35p) ~ mov*sex + log(fam_income) + mom_edu + dad_edu + race | year5 + reg5 + age |0|0)
reg_a <- felm(formula = log(income25_35p) ~ mov*age + log(fam_income) + mom_edu + dad_edu + race| year5 + reg5 |0|0)

stargazer(reg0, reg1, reg2,reg_s,reg_a,
          type = 'latex',
          header = FALSE,
          title = "Mobility Effects on Income (with birth year and region fixed effects)",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','(4)','$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c("Age dummies", "No", "Yes","Yes", "Yes","No"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes","Yes"),
                           c("Region FE", "No", "No","Yes", "Yes","Yes")))

detach(regdata)
```



## Heterogeneity in age

### Table 7: Age groups

```{r results='asis', message=FALSE}
attach(regdata)
log_fixed_reg1 <- felm(formula = log(income25_35p) ~ mov + age_gp12 + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5|0|0)

reg_a1 <- felm(formula = log(income25_35p) ~ mov*age_gp12 + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5|0|0)

log_fixed_reg2 <- felm(formula = log(income25_35p) ~ mov + age_gp6 +age_gp7t8 + age_gp9t10 + age_gp11t12 + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5|0|0)

reg_a2 <- felm(formula = log(income25_35p) ~ mov*age_gp6 +mov*age_gp7t8 + mov*age_gp9t10 + mov*age_gp11t12 + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5|0|0)
stargazer(log_fixed_reg1, reg_a1, log_fixed_reg2, reg_a2,
          type = "latex",
          header = FALSE,
          title = "Mobility effects on  (interacted with Age group)",
          column.labels = c('$(1)$','$(2)$','$(3)$','$(4)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c("Controls","Yes", "Yes", "Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes", "Yes","Yes"),
                           c("Region FE", "Yes", "Yes", "Yes","Yes")))
detach(regdata)

```

## Other specifications

### Table A1: Income at 25, Income at 30 and Income at 35, Avg Income25-30, Avg Income30-35

```{r results='asis', message=FALSE}

regdata <- data %>%
  filter((fam_income > 200) & (income25_35p > 100))
attach(regdata)

reg25_30 <- felm(formula = income25_30p ~ mov + fam_income + mom_edu + dad_edu + sex + race | year5 + age + reg5|0|0)
reg30_35 <- felm(formula = income31_35p ~ mov + fam_income + mom_edu + dad_edu + sex + race | year5 + age + reg5|0|0)
reg25_35 <- felm(formula = income25_35p ~ mov + fam_income + mom_edu + dad_edu + sex + race | year5 + age + reg5|0|0)

reg25_30l <- felm(formula = log(income25_30p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + age + reg5|0|0)
reg30_35l <- felm(formula = log(income31_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + age + reg5|0|0)
reg25_35l <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + age + reg5|0|0)

stargazer(reg25_30, reg30_35, reg25_35, reg25_30l, reg30_35l, reg25_35l,
          type = 'latex',
          header = FALSE,
          title = "Mobility Effects on Income (other specifications)",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$','$(6)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c("Age dummies", "Yes", "Yes","Yes", "Yes","Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes","Yes","Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes","Yes","Yes")))
detach(regdata)
```

### Table 15: Reasons to move
```{r results='asis', message=FALSE}
regdata1 <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) & 
           (((mov==1)&(reason_gp==1))|(mov==0))) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5))
regdata2 <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) & 
           (((mov==1)&(reason_gp==2))|(mov==0))) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5))
regdata3 <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) & 
           (((mov==1)&(reason_gp==3))|(mov==0))) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5))
regdata4 <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) & 
           (((mov==1)&(reason_gp==4))|(mov==0))) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5))

attach(regdata1)
reg1 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5 + age |0|0) # Cluster at current age level
detach(regdata1)

attach(regdata2)
reg2 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5 + age |0|0) # Cluster at current age level
detach(regdata2)

attach(regdata3)
reg3 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5 + age |0|0) # Cluster at current age level
detach(regdata3)

attach(regdata4)
reg4 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5 + age |0|0) # Cluster at current age level
detach(regdata4)

stargazer(reg1, reg2, reg3, reg4,
          type = "latex",
          header = FALSE,
          title = "Mobility effects on labor outcome (Subgroup based on moving reasons)",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c("Reason for moving","Production",
                             "Consumption","Outside reason","Other"),
                          c("Age dummies", "Yes", "Yes","Yes", "Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes")))

```

### Table 13: whether it is a big move
```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100)) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))


regdata1 <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) &
           (((xstate==1)&(mov==1))|(mov==0))) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))

regdata2 <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) &
           (((xstate==0)&(mov==1))|(mov==0))) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))

regdata3 <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) &
           (((xreg==1)&(mov==1))|(mov==0))) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))

regdata4 <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) &
           (((xreg==0)&(mov==1))|(mov==0))) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))

attach(regdata)
fereg <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5 + age |0|0) 
detach(regdata)
attach(regdata1)
xstate_reg1 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5 + age |0|0) 
detach(regdata1)
attach(regdata2)
xstate_reg2 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5 + age |0|0) 
detach(regdata2)
attach(regdata3)
xreg_reg1 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5 + age |0|0) 
detach(regdata3)
attach(regdata4)
xreg_reg2 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race | year5 + reg5 + age |0|0) 
detach(regdata4)

stargazer(fereg, xstate_reg1, xstate_reg2,xreg_reg1, xreg_reg2,
          type = "latex",
          header = FALSE,
          title = "Mobility effects on  labor outcome (Whether move across state/region)",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c("Type of move","Full sample","Across state",
                             "Within state","Across region","Within region"),
                           c("Age dummies", "Yes", "Yes","Yes", "Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes","Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes","Yes")))

```

## Income - IV

### Mom_age results
#### Table 8: Linear mom age & dummy mom age
```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) ) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))

attach(regdata)
baseline <-  felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race| year5 + reg5 + age|0|0) 
stage1_reg1 <- felm(formula = mov ~ mom_age + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
stage2_reg1 <- felm(formula = log(income25_35p) ~ log(fam_income) + dad_edu + mom_edu + sex + race |year5 + reg5 + age| (mov ~ mom_age) |0)

stage1_reg2 <- felm(formula = mov ~ mom_age_gp30 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)

stage2_reg2 <- felm(formula = log(income25_35p) ~ log(fam_income) + dad_edu + mom_edu + sex + race |year5 + reg5 + age| (mov ~ mom_age_gp30) |0)

Fstat0 <- summary(baseline)$F.fstat 
Fstat1 <- summary(stage1_reg1)$F.fstat 
Fstat2 <- summary(stage2_reg1)$F.fstat
Fstat3 <- summary(stage1_reg2)$F.fstat 
Fstat4 <- summary(stage2_reg2)$F.fstat 
stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
stars3 <- ifelse(Fstat3[4]<0.01,"***",ifelse(Fstat3[4]<0.05,"**",ifelse(Fstat3[4]<0.1,"*","")))
stars4 <- ifelse(Fstat4[4]<0.01,"***",ifelse(Fstat4[4]<0.05,"**",ifelse(Fstat4[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars0,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))
note3 <- c(paste(round(Fstat3[1],3),stars3,sep=""))
note4 <- c(paste(round(Fstat4[1],3),stars4,sep=""))

stargazer(baseline, stage1_reg1, stage2_reg1, stage1_reg2, stage2_reg2,
          type = "latex",
          header = FALSE,
          title = "Mom's age as IV",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",
                                   sep=""),note0,note1,note2,note3,note4),
                           c("Age dummies","Yes", "Yes","Yes", "Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes","Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes","Yes")))
detach(regdata)
```
#### Table 18: First stage - discretize
```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) ) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))

attach(regdata)
reg_gp1 <- felm(formula = mov ~ mom_age_gp1 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
reg_gp2 <- felm(formula = mov ~ mom_age_gp2 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
reg_gp3 <- felm(formula = mov ~ mom_age_gp3 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
reg_gp4 <- felm(formula = mov ~ mom_age_gp4 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
reg_gp5 <- felm(formula = mov ~ mom_age_gp5 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)

Fstat0 <- summary(reg_gp1)$F.fstat 
Fstat1 <- summary(reg_gp2)$F.fstat 
Fstat2 <- summary(reg_gp3)$F.fstat
Fstat3 <- summary(reg_gp4)$F.fstat 
Fstat4 <- summary(reg_gp5)$F.fstat 
stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
stars3 <- ifelse(Fstat3[4]<0.01,"***",ifelse(Fstat3[4]<0.05,"**",ifelse(Fstat3[4]<0.1,"*","")))
stars4 <- ifelse(Fstat4[4]<0.01,"***",ifelse(Fstat4[4]<0.05,"**",ifelse(Fstat4[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars0,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))
note3 <- c(paste(round(Fstat3[1],3),stars3,sep=""))
note4 <- c(paste(round(Fstat4[1],3),stars4,sep=""))

screenreg(list(first_stage_reg, second_stage_reg), include.fstatistic = T)
stargazer(reg_gp1, reg_gp2, reg_gp3, reg_gp4, reg_gp5,
          type = "latex",
          header = FALSE,
          title = "Mom's age as IV",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",
                                   sep=""),note0,note1,note2,note3,note4),
                           c("Mom's age group", "20-22", "23-26","27-30", "31-34","35+"),
                           c("Age dummies","Yes", "Yes","Yes", "Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes","Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes","Yes")))
detach(regdata)
```

### Number of regions results
#### Table A5: First stage - discretize
```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) & ((nreg > 0) & (nreg <= 4))) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,nreg))

attach(regdata)
reg_gp1 <- felm(formula = mov ~ nreg + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
reg_gp2 <- felm(formula = mov ~ nreg_dum1 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)

reg_gp3 <- felm(formula = nmov ~ nreg + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
reg_gp4 <- felm(formula = nmov ~ nreg_dum1 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)

Fstat0 <- summary(reg_gp1)$F.fstat 
Fstat1 <- summary(reg_gp2)$F.fstat 
Fstat2 <- summary(reg_gp3)$F.fstat 
Fstat3 <- summary(reg_gp4)$F.fstat 

stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
stars3 <- ifelse(Fstat3[4]<0.01,"***",ifelse(Fstat3[4]<0.05,"**",ifelse(Fstat3[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars0,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))
note3 <- c(paste(round(Fstat3[1],3),stars3,sep=""))

stargazer(reg_gp1,reg_gp2,reg_gp3, reg_gp4,
          type = "latex",
          header = FALSE,
          title = "First stage: Discretized number of regions",
          column.labels = c('$(1)$', '$(2)$','$(3)$', '$(4)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",
                                   sep=""),note0,note1,note2,note3),
                           c("Age dummies","Yes", "Yes","Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes","Yes"),
                           c("Region FE", "Yes", "Yes","Yes","Yes")))
detach(regdata)
```

#### Table A3: Linear nreg & dummy nreg
```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) & ((nreg > 0) & (nreg <= 4))) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,nreg))

attach(regdata)
baseline <-  felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race| year5 + reg5 + age|0|0) 
stage1_reg1 <- felm(formula = mov ~ nreg + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5+age| 0 |0)

stage2_reg1 <- felm(formula = log(income25_35p) ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + reg5+age| (mov ~ nreg) |0)

stage1_reg2 <- felm(formula = mov ~ nreg_dum2 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5+age| 0 |0)

stage2_reg2 <- felm(formula = log(income25_35p) ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + reg5+age| (mov ~ nreg_dum2) |0)

Fstat0 <- summary(baseline)$F.fstat 
Fstat1 <- summary(stage1_reg1)$F.fstat 
Fstat2 <- summary(stage2_reg1)$F.fstat
Fstat3 <- summary(stage1_reg2)$F.fstat 
Fstat4 <- summary(stage2_reg2)$F.fstat 
stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
stars3 <- ifelse(Fstat3[4]<0.01,"***",ifelse(Fstat3[4]<0.05,"**",ifelse(Fstat3[4]<0.1,"*","")))
stars4 <- ifelse(Fstat4[4]<0.01,"***",ifelse(Fstat4[4]<0.05,"**",ifelse(Fstat4[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars0,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))
note3 <- c(paste(round(Fstat3[1],3),stars3,sep=""))
note4 <- c(paste(round(Fstat4[1],3),stars4,sep=""))

stargazer(baseline, stage1_reg1, stage2_reg1, stage1_reg2, stage2_reg2,
          type = "latex",
          header = FALSE,
          title = "nregion as IV",
           column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",
                                   sep=""),note0,note1,note2,note3,note4),
                           c("Age dummies","Yes", "Yes","Yes", "Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes","Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes","Yes")))
detach(regdata)
```

### Number of state results
#### Table A8: First stage - discretize
```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) & (nstate > 0)) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,nstate))

attach(regdata)
reg_gp1 <- felm(formula = mov ~ nstate + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
reg_gp2 <- felm(formula = mov ~ nstate_dum1 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
reg_gp3 <- felm(formula = mov ~ nstate_dum2 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
reg_gp4 <- felm(formula = mov ~ nstate_dum3 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
reg_gp5 <- felm(formula = mov ~ nstate_dum4 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)

Fstat0 <- summary(reg_gp1)$F.fstat 
Fstat1 <- summary(reg_gp2)$F.fstat 
Fstat2 <- summary(reg_gp3)$F.fstat
Fstat3 <- summary(reg_gp4)$F.fstat 
Fstat4 <- summary(reg_gp5)$F.fstat 
stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
stars3 <- ifelse(Fstat3[4]<0.01,"***",ifelse(Fstat3[4]<0.05,"**",ifelse(Fstat3[4]<0.1,"*","")))
stars4 <- ifelse(Fstat4[4]<0.01,"***",ifelse(Fstat4[4]<0.05,"**",ifelse(Fstat4[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars0,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))
note3 <- c(paste(round(Fstat3[1],3),stars3,sep=""))
note4 <- c(paste(round(Fstat4[1],3),stars4,sep=""))

stargazer(reg_gp1, reg_gp2, reg_gp3, reg_gp4, reg_gp5,
          type = "latex",
          header = FALSE,
          title = "nstate as IV",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",
                                   sep=""),note0,note1,note2,note3,note4),
                           c("# of states", "Full sample","1", "2","3", ">=4"),
                           c("Age dummies","Yes", "Yes","Yes", "Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes","Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes","Yes")))
detach(regdata)
```

#### Table A7: Linear nstate & dummy nstate
```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) & (nstate > 0)) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,nstate))

attach(regdata)
baseline <-  felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race| year5 + reg5 + age|0|0) 
stage1_reg1 <- felm(formula = mov ~ nstate + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5+age| 0 |0)

stage2_reg1 <- felm(formula = log(income25_35p) ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + reg5+age| (mov ~ nstate) |0)

stage1_reg2 <- felm(formula = mov ~ nstate_dum4 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5+age| 0 |0)

stage2_reg2 <- felm(formula = log(income25_35p) ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + reg5+age| (mov ~ nstate_dum4) |0)

Fstat0 <- summary(baseline)$F.fstat 
Fstat1 <- summary(stage1_reg1)$F.fstat 
Fstat2 <- summary(stage2_reg1)$F.fstat
Fstat3 <- summary(stage1_reg2)$F.fstat 
Fstat4 <- summary(stage2_reg2)$F.fstat 
stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
stars3 <- ifelse(Fstat3[4]<0.01,"***",ifelse(Fstat3[4]<0.05,"**",ifelse(Fstat3[4]<0.1,"*","")))
stars4 <- ifelse(Fstat4[4]<0.01,"***",ifelse(Fstat4[4]<0.05,"**",ifelse(Fstat4[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars0,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))
note3 <- c(paste(round(Fstat3[1],3),stars3,sep=""))
note4 <- c(paste(round(Fstat4[1],3),stars4,sep=""))

stargazer(baseline, stage1_reg1, stage2_reg1, stage1_reg2, stage2_reg2,
          type = "latex",
          header = FALSE,
          title = "nstate as IV",
           column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",
                                   sep=""),note0,note1,note2,note3,note4),
                           c("Age dummies","Yes", "Yes","Yes", "Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes","Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes","Yes")))
detach(regdata)
```


## Auxillary Regressions
### Table 10: Number of move on Income avg 25-35p

```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100)) %>%
  drop_na(c(nmov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))

attach(regdata)

reg0 <- felm(formula = log(income25_35p) ~ nmov | year5|0|0)
reg1 <- felm(formula = log(income25_35p) ~ nmov + log(fam_income) + mom_edu + dad_edu + sex + race|year5 + age|0|0)
reg2 <- felm(formula = log(income25_35p) ~ nmov + log(fam_income) + mom_edu + dad_edu + sex + race|year5 + reg5 + age|0|0) 
reg3 <- felm(formula = log(income25_35p) ~ nmov + I(nmov^2)+log(fam_income) + mom_edu + dad_edu + sex + race|year5 + reg5 + age|0|0) 
reg4 <- felm(formula = log(income25_35p) ~ nmov1 + nmov2 + nmov3 +nmov4 +log(fam_income) + mom_edu + dad_edu + sex + race|year5 + reg5 + age|0|0)

stargazer(reg0, reg1, reg2,reg3,reg4,
          type = 'latex',
          header = FALSE,
          title = "Mobility Effects on Income (with birth year and region fixed effects)",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$','$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c("Age dummies", "No", "Yes","Yes", "Yes", "Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes", "Yes"),
                           c("Region FE", "No", "No","Yes", "Yes", "Yes")))
detach(regdata)
```
### IV: Mom_age results

#### Table 11: Linear mom age & dummy mom age
```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) ) %>%
  drop_na(c(nmov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))

attach(regdata)
baseline <-  felm(formula = log(income25_35p) ~ nmov + log(fam_income) + mom_edu + dad_edu + sex + race| year5 + reg5 + age|0|0) 
stage1_reg1 <- felm(formula = nmov ~ mom_age + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)
stage2_reg1 <- felm(formula = log(income25_35p) ~ log(fam_income) + dad_edu + mom_edu + sex + race |year5 + reg5 + age| (nmov ~ mom_age) |0)

stage1_reg2 <- felm(formula = nmov ~ mom_age_gp30 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5 + age|0|0)

stage2_reg2 <- felm(formula = log(income25_35p) ~ log(fam_income) + dad_edu + mom_edu + sex + race |year5 + reg5 + age| (nmov ~ mom_age_gp30) |0)

Fstat0 <- summary(baseline)$F.fstat 
Fstat1 <- summary(stage1_reg1)$F.fstat 
Fstat2 <- summary(stage2_reg1)$F.fstat
Fstat3 <- summary(stage1_reg2)$F.fstat 
Fstat4 <- summary(stage2_reg2)$F.fstat 
stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
stars3 <- ifelse(Fstat3[4]<0.01,"***",ifelse(Fstat3[4]<0.05,"**",ifelse(Fstat3[4]<0.1,"*","")))
stars4 <- ifelse(Fstat4[4]<0.01,"***",ifelse(Fstat4[4]<0.05,"**",ifelse(Fstat4[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars0,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))
note3 <- c(paste(round(Fstat3[1],3),stars3,sep=""))
note4 <- c(paste(round(Fstat4[1],3),stars4,sep=""))

stargazer(baseline, stage1_reg1, stage2_reg1, stage1_reg2, stage2_reg2,
          type = "latex",
          header = FALSE,
          title = "Mom's age as IV",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",
                                   sep=""),note0,note1,note2,note3,note4),
                           c("Mom's age group", "20-22", "23-26","27-30", "31-34","35+"),
                           c("Age dummies","Yes", "Yes","Yes", "Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes","Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes","Yes")))
detach(regdata)
```

### nreg results

#### Table A4: Linear nreg & dummy nreg
```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100) & ((nreg > 0) & (nreg <= 4))) %>%
  drop_na(c(nmov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,nreg))

attach(regdata)
baseline <-  felm(formula = log(income25_35p) ~ nmov + log(fam_income) + mom_edu + dad_edu + sex + race| year5 + reg5 + age|0|0) 
stage1_reg1 <- felm(formula = nmov ~ nreg + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5+age| 0 |0)

stage2_reg1 <- felm(formula = log(income25_35p) ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + reg5+age| (nmov ~ nreg) |0)

stage1_reg2 <- felm(formula = nmov ~ nreg_dum2 + log(fam_income) + dad_edu + mom_edu + sex + race| year5 + reg5+age| 0 |0)

stage2_reg2 <- felm(formula = log(income25_35p) ~ sex + race + log(fam_income) + dad_edu + mom_edu |year5 + reg5+age| (nmov ~ nreg_dum2) |0)

Fstat0 <- summary(baseline)$F.fstat 
Fstat1 <- summary(stage1_reg1)$F.fstat 
Fstat2 <- summary(stage2_reg1)$F.fstat
Fstat3 <- summary(stage1_reg2)$F.fstat 
Fstat4 <- summary(stage2_reg2)$F.fstat 
stars0 <- ifelse(Fstat0[4]<0.01,"***",ifelse(Fstat0[4]<0.05,"**",ifelse(Fstat0[4]<0.1,"*","")))
stars1 <- ifelse(Fstat1[4]<0.01,"***",ifelse(Fstat1[4]<0.05,"**",ifelse(Fstat1[4]<0.1,"*","")))
stars2 <- ifelse(Fstat2[4]<0.01,"***",ifelse(Fstat2[4]<0.05,"**",ifelse(Fstat2[4]<0.1,"*","")))
stars3 <- ifelse(Fstat3[4]<0.01,"***",ifelse(Fstat3[4]<0.05,"**",ifelse(Fstat3[4]<0.1,"*","")))
stars4 <- ifelse(Fstat4[4]<0.01,"***",ifelse(Fstat4[4]<0.05,"**",ifelse(Fstat4[4]<0.1,"*","")))
note0 <- c(paste(round(Fstat0[1],3),stars0,sep=""))
note1 <- c(paste(round(Fstat1[1],3),stars1,sep=""))
note2 <- c(paste(round(Fstat2[1],3),stars2,sep=""))
note3 <- c(paste(round(Fstat3[1],3),stars3,sep=""))
note4 <- c(paste(round(Fstat4[1],3),stars4,sep=""))

stargazer(baseline, stage1_reg1, stage2_reg1, stage1_reg2, stage2_reg2,
          type = "latex",
          header = FALSE,
          title = "nregion as IV",
           column.labels = c('$(1)$', '$(2)$', '$(3)$','$(4)$', '$(5)$'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c(paste("F Statistic"," (df = ",Fstat1[2],"; ", Fstat1[3],")",
                                   sep=""),note0,note1,note2,note3,note4),
                           c("Age dummies","Yes", "Yes","Yes", "Yes","Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes","Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes","Yes")))
detach(regdata)
```

### Clustering issue
### Table 19: Income avg 25-35p baseline
```{r results='asis', message=FALSE}
regdata <- data %>% 
  filter((fam_income > 200) & (income25_35p > 100)) %>%
  drop_na(c(mov,fam_income,mom_edu,dad_edu,sex,race,year5,age,reg5,mom_age))

attach(regdata)

reg0 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race|year5 + reg5 + age|0|0) 
reg1 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race|year5 + reg5 + age|0|reg5)
reg2 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race|year5 + reg5 + age|0|age)
reg3 <- felm(formula = log(income25_35p) ~ mov + log(fam_income) + mom_edu + dad_edu + sex + race|year5 + reg5 + age|0|year5)

stargazer(reg0, reg1, reg2, reg3,
          type = 'latex',
          header = FALSE,
          title = "Mobility Effects on Income: Difference in Clustered SE",
          column.labels = c('$(1)$', '$(2)$', '$(3)$','(4)'),
          colnames = FALSE,
          model.numbers = FALSE,
          df = FALSE,
          add.lines = list(c("Clustering level","None","Region","Age","Birth year"),
            c("Clusters","None","4","13","28"),
            c("Age dummies", "Yes", "Yes","Yes", "Yes"),
                          c("Birth Year FE", "Yes", "Yes","Yes", "Yes"),
                           c("Region FE", "Yes", "Yes","Yes", "Yes")))

detach(regdata)
```